CVS Installation und Konfiguration

### 2014-09-22 CM-Scripts/studentuserlist.tex
list of student users

\documentclass[a4paper,9pt,landscape]{scrartcl}
\usepackage[top=1cm,bottom=1cm,left=2cm,right=1cm]{geometry}

@@

@@

\section{CVS-Zug\"ange f\"ur Studenten, Stand: \today}
\begin{longtabu}to 1\textwidth{|l|l|l|l|l|X|l|l|}

@@

\rowcolor{yellow}\cellcolor{red}diplomand1   &alber  &Thomas Alber    &th.alber@loop.de      &Javagui/viewer/queryconstruction2 &17.06.13     &\\

@@

\cellcolor{red}            &uchdorf                  &Thomas Uchdorf  &                      &Algebras/OSM                      &08.02.11     &05.03.12\\
\cellcolor{red}            &vjohn                    &Volker John     &                      &Algebras/OptAux                   &             &08.02.11\\

@@

@@

\cellcolor{red}            &fpanse                   &Frank Panse     &                      &Algebras/SymbolicTrajectory       &21.12.10     &05.03.12\\

@@

\cellcolor{red}            &nvoget                   &Nicolai Voget   &                      &Algebras/OrderedRelation          &             &21.12.10\\
\rowcolor{yellow}\cellcolor{red}diplomand3   &eckebre&Jens Eckebrecht &jens@eckebrecht.de    &Algebras/RobustPlaneSweep         &21.12.12     & \\
\cellcolor{red}            &kubusch                  &Rico Kubusch    &rico.kubusch@bka.bund.de&                                &21.06.11     &21.12.12\\
\cellcolor{red}            &bponeleit                &Burkhard Poneleit&                     &Optimizer/Subqueries              &             &08.02.11\\
\rowcolor{yellow}\cellcolor{red}diplomand4   &walther&Daniel Walther  &da.walther@gmx.de     &Tools/SecondoPostGIS              &22.02.13     &\\
\cellcolor{red}            &kkoch                    &Katja Koch      &katjakoch1@googlemail.com&Algebras/RobustGeometry        &02.01.12     &21.12.12\\
\cellcolor{red}            &geduldig                 &Jochen Geduldig &                      &Algebras/NestedRelation2          &08.09.10     &02.01.12\\
\cellcolor{red}            &kteufel                  &Klaus Teufel    &                      &Algebras/NestedRelation           &             &08.09.10\\

@@

\cellcolor{red}            &totim                    &Tobias Timmerscheidt&                  &Algebras/DistributedRelation      &15.01.10     &16.02.11\\

@@

@@

\cellcolor{red}            &sjung                    &Sven Jungnickel &                      &Algebras/ExtRelation2             &             &08.02.11\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand7   &steigerk&Kristina Steiger&tinasteiger@gmx.net  &WebGui                            &06.05.13     &\\
\cellcolor{red}            &geisbues                 &Simon Geisbuesch&simon.geisbuesch@o2online.de&Algebras/SpatialJoin2       &14.11.11     &21.12.12\\
\cellcolor{red}            &zdahmen                  &Zoryana Dahmen-Lobur&                  &/DahmenLobur                      &20.10.10     &08.02.11\\
\rowcolor{yellow}\cellcolor{red}diplomand8   &kuepper&Michael K\"upper&kuepper.michael@gmail.com&AndroidGui                     &06.05.13     &\\

@@

\cellcolor{red}            &linsenme                 &Linsenmeier     &                      &Algebras/SpatialJoin \& Algebras/NearestNeighbour& &08.02.11\\

@@

@@

\cellcolor{red}            &whoffmann                &Walter Hoffmann &                      &secondo\_Whoff                    &01.02.10     &08.02.11\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand10  &dbecker&Dirk Becker     &tyr@tyrbedarf.de      &Algebras/Cluster2                 &19.06.13     &\\
\cellcolor{red}            &willmes                  &Gero Willmes    &student@harpspieler.de&Optimizer/LargeQueries            &29.11.11     &21.12.12\\
\cellcolor{red}            &herkert                  &A. Herkert      &                      &LargeQueries                      &01.03.10     &08.02.11\\
\rowcolor{yellow}\cellcolor{red}diplomand11  &schroeer&Susanne Schröer&susanne@team-schroeer.com&(noch keins)                   &19.08.13     &\\

@@

@@

\cellcolor{red}            &danbro                   &Daniel Brockmann&                      &Algebras/UGrid                    &14.04.10     &08.02.11\\

@@

@@

\cellcolor{green}diplomand12&mtirtasana              &Matthias Tirtasana&matthias.tirtasana@science-computing.de&OptParser      &05.03.12     &21.12.12\\

@@

\cellcolor{green}          &wrede                    &Nina Wrede      &                      &Algebras/Network2 \& Algebras/TemporalNet2&15.06.10&02.01.12\\

@@

@@

\rowcolor{yellow}\cellcolor{green}diplomand13&nidzwetzki&Jan Nidzwetzki&knidzwetzki@gmx.de   &Algebras/CostEstimation           &18.04.12     &\\

@@

@@

\cellcolor{green}diplomand14&flehmann                &Frank Lehmann   &fraleco@gmx.de        &Algebras/SymbolicTrajectory2      &23.04.12     &12.12.12\\
\rowcolor{yellow}\cellcolor{red}diplomand15&nvkempen &Nicolai van Kempen&nikolaivank@googlemail.com&Optimizer/NestedRelations \& Optimizer/MemoryAllocation&24.04.12&\\
\cellcolor{green}diplomand16&jmoeller                &Jasmin Moeller  &jasminmoeller@gmx.de  &Algebras/Cluster2                 &28.06.12     &21.12.12\\
\rowcolor{yellow}\cellcolor{red}diplomand17&ofeuer   &Oliver Feuer    &ofeuer\_informatik@yahoo.de&Algebras/Region2 \& MovingRegion3&11.10.12 &\cellcolor{red}Laptop\\
\rowcolor{yellow}\cellcolor{red}diplomand18&sfuhs    &Svenja Fuhs     &svenja.fuhs@t-online.de&Algebras/Precise2D               &29.10.12     &\\

@@

@@

\cellcolor{green}diplomand20&                        &                &                      &                                  &             &\\

@@

@@

\end{longtabu}
\end{document}

>>>>

\documentclass[a4paper,8pt,landscape]{scrartcl}
\usepackage[top=1cm,bottom=1cm,left=1cm,right=1cm]{geometry}

@@

% Next: 12

@@

% \section{CVS-Zug\"ange f\"ur Studenten, Stand: \today}
\begin{longtabu}to 1\textwidth{|l|l|l|l|l|l|l|l|}

@@

\rowcolor{yellow}\cellcolor{red}diplomand1   &alber  &Thomas Alber    &th.alber@loop.de      &Javagui/viewer/queryconstruction2 \& Tools/TypeMap &17.06.13     &\\

@@

% \cline{2-7}
% \cellcolor{red}            &uchdorf                  &Thomas Uchdorf  &                      &Algebras/OSM                      &08.02.11     &05.03.12\\
% \cline{2-7}
% \cellcolor{red}            &vjohn                    &Volker John     &                      &Algebras/OptAux                   &             &08.02.11\\

@@

% \cline{2-7}
% \cellcolor{red}            &fpanse                   &Frank Panse     &                      &Algebras/SymbolicTrajectory       &21.12.10     &05.03.12\\
% \cline{2-7}
% \cellcolor{red}            &nvoget                   &Nicolai Voget   &                      &Algebras/OrderedRelation          &             &21.12.10\\
\rowcolor{yellow}\cellcolor{red}diplomand3   &njaeckel&Natalie J\"ackel&natalie.jaeckel@lupusalpha.de&Algebras/DBScan           &12.03.14     &\\

@@

\cellcolor{red}            &eckebre                  &Jens Eckebrecht &jens@eckebrecht.de    &Algebras/RobustPlaneSweep         &21.12.12     &12.03.14\\
% \cline{2-7}
% \cellcolor{red}            &kubusch                  &Rico Kubusch    &rico.kubusch@bka.bund.de&                                &21.06.11     &21.12.12\\
% \cline{2-7}
% \cellcolor{red}            &bponeleit                &Burkhard Poneleit&                     &Optimizer/Subqueries              &             &08.02.11\\
\rowcolor{yellow}\cellcolor{red}diplomand4 &irusskaya&Irina Russkaya  &irina.russkaya@fernuni-hagen.de&WebGui2                  &05.06.14     &\\

@@

\cellcolor{red}            &walther                  &Daniel Walther  &da.walther@gmx.de     &Tools/SecondoPostGIS              &22.02.13     &05.06.14\\
% \cline{2-7}
% \cellcolor{red}            &kkoch                    &Katja Koch      &katjakoch1@googlemail.com&Algebras/RobustGeometry        &02.01.12     &21.12.12\\
% \cline{2-7}
% \cellcolor{red}            &geduldig                 &Jochen Geduldig &                      &Algebras/NestedRelation2          &08.09.10     &02.01.12\\
% \cline{2-7}
% \cellcolor{red}            &kteufel                  &Klaus Teufel    &                      &Algebras/NestedRelation           &             &08.09.10\\

@@

% \cline{2-7}
% \cellcolor{red}            &totim                    &Tobias Timmerscheidt&                  &Algebras/DistributedRelation      &15.01.10     &16.02.11\\

@@

% \cline{2-7}
% \cellcolor{red}            &sjung                    &Sven Jungnickel &                      &Algebras/ExtRelation2             &             &08.02.11\\
\rowcolor{yellow}\cellcolor{red}diplomand7 &rsteinbrueck&René Steinbrück&rene.steinbrueck@fernuni-hagen.de&                     &16.06.14     &\\

@@

\cellcolor{red}            &steigerk                 &Kristina Steiger&tinasteiger@gmx.net   &WebGui                            &06.05.13     &\\
% \cline{2-7}
% \cellcolor{red}            &geisbues                 &Simon Geisbuesch&simon.geisbuesch@o2online.de&Algebras/SpatialJoin2       &14.11.11     &21.12.12\\
% \cline{2-7}
% \cellcolor{red}            &zdahmen                  &Zoryana Dahmen-Lobur&                  &/DahmenLobur                      &20.10.10     &08.02.11\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand8  &kuepper &Michael K\"upper&kuepper.michael@gmail.com&AndroidGui                     &06.05.13     &\\

@@

% \cline{2-7}
% \cellcolor{red}            &linsenme                 &Linsenmeier     &                      &Algebras/SpatialJoin \& Algebras/NearestNeighbour& &08.02.11\\

@@

% \cline{2-7}
% \cellcolor{red}            &whoffmann                &Walter Hoffmann &                      &secondo\_Whoff                    &01.02.10     &08.02.11\\
\rowcolor{yellow}\cellcolor{red}diplomand10 &cmotzek &Carsten Motzek  &carsten.motzek@gmail.com&                                &23.06.14     & \\

@@

\cellcolor{red}            &dbecker                  &Dirk Becker     &tyr@tyrbedarf.de      &Algebras/Cluster2                 &19.06.13     &23.06.14\\
% \cline{2-7}
% \cellcolor{red}            &willmes                  &Gero Willmes    &student@harpspieler.de&Optimizer/LargeQueries            &29.11.11     &21.12.12\\
% \cline{2-7}
% \cellcolor{red}            &herkert                  &A. Herkert      &                      &LargeQueries                      &01.03.10     &08.02.11\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand11 &schroeer&Susanne Schröer&susanne@team-schroeer.com&Algebras/MRegionOps2            &19.08.13     &\\

@@

% \cline{2-7}
% \cellcolor{red}            &danbro                   &Daniel Brockmann&                      &Algebras/UGrid                    &14.04.10     &08.02.11\\
\rowcolor{yellow}\cellcolor{red}diplomand12 &slinne  &Sascha Linne    &sl@linne.de           &Optimizer/Linne                   &07.07.14     &\\

@@

\cellcolor{red}            &ghaase                   &Guido Haase     &guido.haase@db.com    &Algebras/KeywordRTree             &19.11.13     &07.07.14\\
%\cline{2-7}
%\cellcolor{red}            &mtirtasana               &Matthias Tirtasana&matthias.tirtasana@science-computing.de&OptParser      &05.03.12     &21.12.12\\
%\cline{2-7}
%\cellcolor{red}            &wrede                    &Nina Wrede      &                      &Algebras/Network2 \& Algebras/TemporalNet2&15.06.10&02.01.12\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand13 &teutsch &Michael Teutsch &m.h.teutsch@googlemail.com&Optimizer/ParallelHadoop      &22.10.13     &\\
\cellcolor{red}            &nidzwetzki               &Jan Nidzwetzki  &knidzwetzki@gmx.de    &Algebras/CostEstimation           &18.04.12     &21.10.13\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand14 &stockschlaeder&Hermann Stockschl\"ader&h.stockschlaeder@web.de&                    &14.11.13     &\\

@@

\cellcolor{red}            &flehmann                 &Frank Lehmann   &fraleco@gmx.de        &Algebras/SymbolicTrajectory2      &23.04.12     &12.12.12\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand15 &jstehmann&Jana Stehmann  &jana.stehmann@gmx.de  &Algebras/GIS                      &25.10.13     &\\
\cellcolor{red}            &nvkempen                 &Nicolai van Kempen&nikolaivank@googlemail.com&Optimizer/NestedRelations \& Optimizer/MemoryAllocation&24.04.12&25.10.13\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand16 &mgoram  &Mandy Goram     &m.goram@gmx.net       &students/Goram                    &25.02.14     &\\
\cellcolor{red}            &jmoeller                 &Jasmin Moeller  &jasminmoeller@gmx.de  &Algebras/Cluster2                 &28.06.12     &21.12.12\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand17 &mhaug   &Marius Haug     &marius.haug@gmx.de    &Algebras/Optics                   &12.03.14     &\\
\cellcolor{red}            &ofeuer                   &Oliver Feuer    &ofeuer\_informatik@yahoo.de&Algebras/Region2 \& MovingRegion3&11.10.12 &\cellcolor{red}Laptop\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand18&ffahrmeier&Franz Fahrmeier&franz\_fa@gmx.net     &Javagui/viewer/spacetimecube      &05.03.14     &\\
\cellcolor{red}            &sfuhs                    &Svenja Fuhs     &svenja.fuhs@t-online.de&Algebras/Precise2D               &29.10.12     &05.03.14\\

@@

\rowcolor{yellow}\cellcolor{red}diplomand20&nidzwetzki&Jan Nidzwetzki &knidzwetzki@gmx.de    &Algebras/Cassandra                &12.02.14&\\

@@

\cellcolor{green}diplomand21\\

@@

\cellcolor{green}diplomand22\\

@@

\cellcolor{green}diplomand23\\
\cellcolor{green}diplomand24\\
\cellcolor{green}diplomand25\\
\cellcolor{green}diplomand26\\
\cellcolor{green}diplomand27\\
\cellcolor{green}diplomand28\\
\cellcolor{green}diplomand29\\
\cellcolor{green}diplomand30\\

\end{longtabu}
\end{document}
